---
title: "visualiztion_1"
author: "Aiying Huang"
date: "2023-09-28"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
library(patchwork)
```

# 格式设置
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USW00022534 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Let's make a plot!

```{r}
ggplot(weather_df,aes(x=tmin,y=tmax))+
  geom_point()
```

pipes and stuff

```{r}
weather_df|>
  filter(name=="CentralPark_NY")|>
  ggplot(aes(x=tmin,y=tmax))+
  geom_point()
  
```

```{r}
ggp_nyc_weather=
  weather_df|>
  filter(name=="CentralPark_NY")|>
  ggplot(aes(x=tmin,y=tmax))+
  geom_point()
```

## Fancy plot

```{r}
ggplot(weather_df,aes(x=tmin,y=tmax,color=name))+
  geom_point()+
  geom_smooth()
```

```{r}
ggplot(weather_df,aes(x=tmin,y=tmax))+
  geom_point(aes(color=name))+
  geom_smooth()
```

```{r}
ggplot(weather_df,aes(x=tmin,y=tmax))+
  geom_point(aes(color=name),alpha=0.3)+
  geom_smooth(se=FALSE)#standar error
```

Plot with facets

```{r}
ggplot(weather_df,aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.3)+
  geom_smooth()+
  facet_grid(. ~name)
# alpha order
```

Let's try a different plot

```{r}
ggplot(weather_df,aes(x=date,y=tmax,color=name))+
  geom_point(aes(size=prcp),alpha=.3)+
  geom_smooth()+
  facet_grid(. ~name)
```

try assigning a specific color

```{r}
weather_df|>
  filter(name=="CentralPark_NY")|>
  ggplot(aes(x=date,y=tmax))+
  geom_point(color="blue")
```

```{r}
weather_df|>
  filter(name!="CentralPark_NY")|>
  ggplot(aes(x=date,y=tmax,color=name))+
  geom_point()
```

```{r}
weather_df|>
  filter(name!="CentralPark_NY")|>
  ggplot(aes(x=date,y=tmax,color=name))+
  geom_point(alpha=.3,size=.5)
```

hex plot :-)

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax))+
  geom_hex()
```
## univariate plotting

histogram

```{r}
ggplot(weather_df,aes(x=tmax))+
  geom_histogram()
```
```{r}
ggplot(weather_df,aes(x=tmax,color=name,fill=name))+
  geom_histogram()
```


```{r}
ggplot(weather_df,aes(x=tmax,color=name,fill=name))+
  geom_histogram(position="dodge")
```

let's use a density plot

```{r}
ggplot(weather_df,aes(x=tmax,fill=name))+
  geom_density(alpha=.3,adjust=.75)
```
```{r}
ggplot(weather_df,aes(x=tmax,fill=name))+
  geom_density(alpha=.3,adjust=2)
```

using boxplots!!

```{r}
ggplot(weather_df,aes(y=tmax,x=name))+
  geom_boxplot()
```

violin plots?

```{r}
ggplot(weather_df,aes(y=tmax,x=name))+
  geom_violin()
```

ridge plot

```{r}
ggplot(weather_df,aes(x=tmax,y=name))+
  geom_density_ridges()
```


```{r}
weather_df|>
  filter(name=="Molokai_HI")|>
  ggplot(aes(x=date,y=tmax))+
  geom_line(alpha=.5)+
  geom_point(alpha=.5)
```

## saving and embedding plots

```{r}
ggp_weather=
weather_df|>
  ggplot(aes(x=tmin,y=tmax))+
  geom_point()

ggsave("Results/ggp_weather.pdf",ggp_weather)
```

```{r}
ggp_weather
```


```{r,fig.width=12,fig.height=12}
ggp_weather
```

```{r,fig.width=6,fig.asp=.6}
ggp_weather
```

## same plot from last time

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  )
```
```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  )+
  scale_x_continuous(
    breaks=c(-15,0,15),
    labels=c("-15 C","0","15")
  )+
  scale_y_continuous(
    position="right",
    trans="sqrt"
  )
```

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  )+
  scale_x_continuous(
    breaks=c(-15,0,15),
    labels=c("-15 C","0","15")
  )+
  scale_y_continuous(
    position="right",
    limits=c(20,30)
  )
```

what about colors...

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  ) +
  viridis::scale_color_viridis(discrete=TRUE)
```


## Themes

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  ) +
  viridis::scale_color_viridis(discrete=TRUE)+
  theme_bw()+#the order here makes a difference, cannot be changed
  theme(legend.position="bottom")
```

```{r}
weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  labs(
    title="Temperature plot",
    x="Mim daily temp (Degreesc)",
    y="Max daily temp",
    color="Location",
    caption="Max vs min daily temp in three locations;data from moaa"
  ) +
  viridis::scale_color_viridis(discrete=TRUE)+
  theme_minimal()+#the order here makes a difference, cannot be changed
  theme(legend.position="bottom")
```

##选择使用"viridis"颜色主题的原因是因为它在数据可视化中具有一些优点，特别是在表示渐变数据时。以下是一些选择"viridis"颜色主题的原因：

良好的可读性："viridis"颜色主题经过精心设计，确保颜色在不同亮度和饱和度下都能够清晰可辨。这使得图表更容易阅读，尤其是在印刷品和屏幕上。

高对比度："viridis"颜色主题具有高对比度，可以凸显数据中的细微变化。这对于强调趋势和差异非常有帮助。

鉴别度高："viridis"颜色主题的不同颜色之间的鉴别度很高，这意味着您可以在不同的数据系列之间轻松区分。

适用于色盲："viridis"颜色主题考虑了色盲人士，确保即使在色觉有问题的人也能正确解释图表。

兼容性强："viridis"颜色主题可以应用于各种数据类型和图表类型，包括散点图、线图、热图等。

总之，"viridis"颜色主题被认为是一种有效的选择，因为它提供了良好的可视效果，有助于传达数据的重要信息，同时考虑了观众的可读性和色盲问题。




## data argument...

```{r}
weather_df|>
  ggplot(aes(x=date,y=tmax))+
  geom_point(aes(color=name))+
  geom_smooth()
```

```{r}
weather_df|>
  ggplot(aes(x=date,y=tmax,color=name))+
  geom_point()+
  geom_smooth()
```
```{r}
nyc_weather_df=
  weather_df|>
  filter(name=="CentralPark_NY")
hawaii_weather_df=
  weather_df|>
  filter(name=="Molokai_HI")

ggplot(nyc_weather_df,aes(x=date,y=tmax,color=name))+
  geom_point()+
  geom_line(data=hawaii_weather_df)
##process the data before plot is always a good choice
```
## `patchwork`


```{r}
weather_df|>
  ggplot(aes(x=date,y=tmax,color=name))+
  geom_point()+
  facet_grid(.~name)
##facet is used to duplicate the same type of plots 
```

```{r}
ggp_temp_scatter=
  weather_df|>
  ggplot(aes(x=tmin,y=tmax,color=name))+
  geom_point(alpha=.5)+
  theme(legend.position="none")

ggp_prcp_density=
  weather_df|>
  filter(prcp>25)|>
  ggplot(aes(x=prcp,fill=name))+
  geom_density(alpha=.5)+
  theme(legend.position="none")

ggp_tmax_date=
  weather_df|>
  ggplot(aes(x=date,y=tmax,color=name))+
  geom_point()+
  geom_smooth(se=FALSE)+
  theme(legend.position="bottom")


(ggp_temp_scatter+ggp_prcp_density)/ggp_tmax_date
```

## data manipulation

```{r}
weather_df|>
  ggplot(aes(x=name,y=tmax))+
  geom_boxplot()
weather_df|>
  mutate(
    name=fct_relevel(name,c("Molokai_HI","CentralPark_NY","Waterhole_WA"))
  )|>
  ggplot(aes(x=name,y=tmax))+
  geom_boxplot()
## ggplot will convert the chr to fact variable by alpha ording

weather_df|>
  mutate(
    name=fct_reorder(name,tmax)
  )|>
  ggplot(aes(x=name,y=tmax,fill=name))+
  geom_violin()
```

## complicate FAS plot

```{r}
litters_df=
  read_csv("./Data/FAS_litters.csv")|>
  janitor::clean_names()|>
  separate(group,into=c("dose","day_of_tx"),sep=3)

pups_df=
  read_csv("./Data/FAS_pups.csv")|>
  janitor::clean_names()

fas_df=
  left_join(pups_df,litters_df,by="litter_number")
fas_df|>
  select(dose,day_of_tx,starts_with("pd"))|>
  pivot_longer(
    pd_ears:pd_walk,
    names_to="outcome",
    values_to="pn_day"
  )|>
  drop_na()|>
  mutate(outcome=fct_reorder(outcome,pn_day))|>
  ggplot(aes(x=dose,y=pn_day))+
  geom_violin()+
  facet_grid(day_of_tx~outcome)
```




































